---
title: "gross_graph"
author: "Marie Rivers"
date: "8/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)

library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
library(ggExtra)
library(ggbeeswarm)
```

```{r}
space_launch <- read_csv(here("data", "space_launches.csv"))
```

```{r}
unique(space_launch$type)
unique(space_launch$agency)
```

```{r}
agency_type <- space_launch %>% 
  count(agency_type, launch_year) %>% 
  filter(agency_type != "#VALUE!")
  
```


```{r}
gross_graph <- ggplot(data = agency_type, aes(x = launch_year, y = n)) +
  geom_line(aes(color = agency_type),
             size = 3) +
  theme(panel.background = element_rect(fill = "azure2", color = "darkgoldenrod2", size = 5),
        plot.background = element_rect(fill = "cornflowerblue", color = "purple", size = 3),
        axis.text = element_text(color = "blue3", size = 15, angle = -15),
        panel.grid = element_line(color = "orange", size = 1.5)) +
  labs(title = "Space Launches by Agency Type",
       x = "earth year",
       y = "number of launches")

ggsave(here("figs", "gross_graph_marie.jpg"), plot = gross_graph)
```
       
ggplot(data = lizards, aes(x = total_length, y = weight)) +
  geom_point() +
  theme(panel.background = element_rect(fill = "yellow", color = "purple", size = 10),
        panel.grid.major.x = element_line(color = "red", size = 2), # most specific command wins
        panel.grid.major = element_line(color = "blue"),
        panel.grid.major.y = element_line(color = "orange", size = 1),
        plot.background = element_rect(fill = "cyan4"),
        axis.text.x = element_text(color = "orange"),
        axis.title = element_text(color = "yellow", size = 12))
# use `panel.grid = element_blank()` for no grid lines  
# panel is about where the data is shown
# plot is the larger background
